---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# bindr [![Travis-CI Build Status](https://travis-ci.org/krlmlr/bindr.svg?branch=master)](https://travis-ci.org/krlmlr/bindr) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/krlmlr/bindr?branch=master&svg=true)](https://ci.appveyor.com/project/krlmlr/bindr) [![Coverage Status](https://img.shields.io/codecov/c/github/krlmlr/bindr/master.svg)](https://codecov.io/github/krlmlr/bindr?branch=master)


Active bindings in R are much like properties in other languages:
They look like a variable,
but querying or setting the value triggers a function call.
They can be created in R via
[`makeActiveBinding()`](https://www.rdocumentation.org/packages/base/versions/3.3.1/topics/bindenv),
but with this API the function used to compute or change the value of a binding cannot take additional arguments.
The `bindr` package faciliates the creation of active bindings that are linked to a function that receives the binding name,
and an arbitrary number of additional arguments.


## Installation

You can install `bindr` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("krlmlr/bindr")
```

## Example

For illustration, the `append_random()` function is used,
which appends a separator (a dash by default) and a random letter
to its input.

```{r}
set.seed(20161510)
append_random <- function(x, sep = "-") {
  message("Evaluating append_random(sep = ", deparse(sep), ")")
  paste(x, sample(letters, 1), sep = sep)
}

append_random("a")
append_random("X", sep = "+")
```

In this example, we create an environment that contains bindings
for all lowercase letters, which are evaluated with `append_random()`.
As a result, a dash and a random letter are appended to the name of the binding:

```{r}
library(bindr)
env <- create_env(letters, append_random)
ls(env)
env$a
env$a
env$a
env$c
env$Z
```

Bindings can also be added to existing environments:

```{r}
populate_env(env, LETTERS, append_random, "+")
env$a
env$Z
```

Both named and unnamed arguments are supported:

```{r}
create_env("binding", paste, "value", sep = "-")$binding
```

A parent environment can be specified for creation:

```{r}
env2 <- create_env("a", identity, .enclos = env)
env2$a
env2$b
get("b", env2)
```

The bindings by default have access to the calling environment:

```{r}
create_local_env <- function(names) {
  paste_with_dash <- function(...) paste(..., sep = "-")
  binder <- function(name, append) paste_with_dash(name, append)
  create_env(names, binder, append = "appending")
}

env3 <- create_local_env("a")
env3$a
```

All bindings are read-only:

```{r failing, error=TRUE}
env3$a <- NA
env3$a <- NULL
```


Existing variables or bindings are not overwritten:

```{r overwrite, error=TRUE}
env4 <- as.environment(list(a = 5))
populate_env(env4, quote(b), identity)
ls(env4)
populate_env(env4, letters, identity)
```


Because active bindings must be R functions,
a native C++ interface is not very useful.
Instead, use an exported Rcpp function,
possibly with `rng = false` if performance matters.
The following C++ module exports a function `change_case(to_upper = FALSE)`,
which is bound against in R code later.

```{Rcpp cpp-mod, cache = TRUE}
#include <Rcpp.h>

#include <algorithm>
#include <string>

using namespace Rcpp;

// [[Rcpp::export(rng = FALSE)]]
SEXP change_case(Symbol name, bool to_upper = false) {
  std::string name_string = name.c_str();
  std::transform(name_string.begin(), name_string.end(),
                 name_string.begin(), to_upper ? ::toupper : ::tolower);
  return CharacterVector(name_string);
}
```

Binding from R:

```{r}
env <- create_env(as.name("__ToLower__"), change_case)
populate_env(env, as.name("__tOuPPER__"), change_case, TRUE)
ls(env)
env$`__ToLower__`
get("__tOuPPER__", env)
```

## License

MIT (c) 2016 Kirill Müller.
